### 2022-03-03 README.Rmd
Update readme, update Dockerfile.

```{r metadata-manuscript, echo = FALSE, include=FALSE}
# Manuscript metadata
manuscript1_yaml <- rmarkdown::yaml_front_matter("analysis/paper/001-paper-main.Rmd")
manuscript2_yaml <- rmarkdown::yaml_front_matter("analysis/paper/001-reply-main.Rmd")

@@

manuscript1$doi <-
  manuscript1_yaml$doi %>%
  paste0(".")
```

@@

> Henning Teickner and Klaus-Holger Knorr, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for "`r manuscript1_yaml$title`" and "`r manuscript2_yaml$title`"_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

You can download the compendium as a zip from from this URL: <https://doi.org/> ---todo

@@

The [Dockerfile](Dockerfile) provides instructions how to build a Docker image from the Dockerfile and how to run the image in a Docker container. It occupies disk space of ~6 Gb.

>>>>

```{r metadata-manuscript, echo = FALSE, include=FALSE}
# Manuscript metadata
manuscript1_yaml <- rmarkdown::yaml_front_matter("analysis/paper/001-paper-main.Rmd")
manuscript2_yaml <- rmarkdown::yaml_front_matter("analysis/paper/002-reply-main.Rmd")

@@

manuscript1$doi <-
  manuscript1_yaml$doi %>%
  paste0(".")

# manuscript2
manuscript2 <- list()
manuscript2$authors <- "Henning Teickner and Klaus-Holger Knorr"

manuscript2$year <- 
  paste0("(",  eval(parse(text = stringr::str_extract(manuscript2_yaml$date, pattern = "^\\d+"))), "):")

manuscript2$title <-
  manuscript2_yaml$title %>%
  paste0(".")

manuscript2$journal <-
  eval(parse(text = manuscript2_yaml$journal %>% stringr::str_remove("^`r ") %>% stringr::str_remove("`$"))) %>%
  names()

manuscript2$doi <-
  manuscript2_yaml$doi %>%
  paste0(".")
```

@@

> Henning Teickner and Klaus-Holger Knorr, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for "`r manuscript1_yaml$title`" and "`r manuscript2_yaml$title`"_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://github.com/henningte/hklmirs/>

@@

You can download the compendium as a zip from from this URL: <https://github.com/henningte/hklmirs/>

@@

The [Dockerfile](Dockerfile) provides instructions how to build a Docker image from the Dockerfile and how to run the image in a Docker container. It occupies disk space of ~7 Gb.
